HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-01-26 LaTeX/ms.tex
Douglas Scott comments

\title{HerMES: Spatially resolved ALMA Imaging of {\it
Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  Combined with our previous work on brighter {\it
    Herschel} sources, the lens models presented here constrain the shape of
    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov Chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
    break down into multiple ALMA counterparts, consistent with previous
    research indicating that the multiplicity rate is high in bright sources
    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
    our {\it Herschel} targets are located much closer to each other than ALMA
    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
    Theoretical models underpredict the excess in number of sources with small
    separations seen in our ALMA sample.  The high multiplicity rate and low
    projected separations between sources seen in our sample argue in favor of
    interactions and mergers plausibly driving both the prodigious emission
    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
    8\,$mJy.

@@

Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
(sub-mm) wavelengths are generally known as dusty star-forming galaxies
(DSFGs).  They cover a wide range in redshift from $z \sim 0.5$ to $z > 6$
\citep{2005ApJ...622..772C, Casey:2012qy, Messias:2014fk, Riechers:2013lr},
with a significant component at $z \sim 2$ \citep{Casey:2012uq,
Bothwell:2013lr}, when they represent the most FIR-luminous objects in
existence during this epoch.   They are signposts of significant over-densities
\citep{Daddi:2009qy, Capak:2011qy} \citep[c.f.][]{Robson:2014xy} and
likely represent the formative stages of the most massive elliptical galaxies
found in the local Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.
Moreover, they constitute an important component of the overall galaxy
population at $z \sim 2$ \citep[e.g.,][]{Magnelli:2011ul}, when the
star-formation rate density in the Universe peaked
\citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.

@@

We here present Atacama Large Millimeter/submillimeter Array (ALMA) Cycle~0
imaging at 870$\,\mu$m of a sample of 29 HerMES DSFGs.
%Our targets were selected to be significantly fainter than those reported in
%\citet{Bussmann:2013lr}, so they include a larger number of unlensed or weakly
%lensed ($\mu_{870} < 2$) sources.  
Three aspects of our dataset make it uniquely suited to improving our
understanding of the bright end of the intrinsic DSFG luminosity function.
First, the sample occupies a distinct regime in flux density between the
brightest {\it Herschel} DSFGs (almost all of which are lensed) and much
fainter DSFGs found in ground-based surveys \citep[most of which are expected
to be unlensed; e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely
sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
\citep[such is not the case in previous similar studies with shallower imaging;
e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
angular resolutions are $0\farcs45$ and nearly all sources detected by ALMA are
spatially resolved.

We also obtained Gemini-South optical imaging to complement our existing array
of ancillary multi-wavelength imaging.  We use those data in this paper to
identify lensing galaxies which are typically early-types with little on-going
star-formation and therefore exhibit very weak sub-mm emission.

In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
Gemini-South imaging.  Section~\ref{sec:modelfits} presents model fitting
methodology and model fits to all ALMA sources (lensed and unlensed) using {\sc
uvmcmcfit}, a publicly available
\footnote{https://github.com/sbussmann/uvmcmcfit} modified version of the
visibility plane lens modeling software used in \citet{Bussmann:2012lr,
Bussmann:2013lr}.  Results on the effect of lensing on the observed properties
of the {\it Herschel} DSFGs in our sample as well as the multiplicity rate and
typical angular separation between sources after delensing the ALMA sources
appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
$\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
end of the DSFG luminosity function in Section~\ref{sec:discuss}.  Finally, we
present our conclusions in Section~\ref{sec:conclusions}.

@@

The starting point for the sample selection is source extraction and
photometry.  Sources are detected using the {\sc StarFinder} code
\citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images
\citep{Wang:2014lr}.
Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},
which allocates flux density based on the 250$\, \mu$m position priors from
{\sc StarFinder}.

Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.
The sample was originally selected to be a complete, flux-limited set of
objects satisfying $S_{500} > 95 \, {\rm mJy}$ that are not known radio AGN,
nearby late type galaxies, or Galactic emission.  The intention was to assemble
the largest possible sample of lenses in the HerMES fields that are accessible
to ALMA.  However, the original selection was based on the HerMES ``V5''
catalog because this was the only one available at the time of the ALMA Cycle~0
deadline.  Subsequently, improved efforts to deblend SPIRE photometry at
$500\,\mu$m were introduced that led to the development of the ``V21'' catalog
that formed the basis of the lens selection criteria used in
\citet{Wardlow:2013lr}.  A number of objects in the sample in this paper have
significantly lower $S_{500}$ values in the V21 catalog, indicating that their
$S_{500}$ in the V5 catalog was boosted by blending with nearby sources rather
than by gravitational lensing.  For this reason, the objects in this sample
comprise a combination of lenses and blends of multiple sources.

@@

Figure~\ref{fig:sample} shows that the ALMA sample is set clearly apart from the
very bright {\it Herschel} DSFGs that are selected to have $S_{500} > 100 \,
$mJy and have been shown to be almost entirely lensed DSFGs
\citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast, the
sample in this paper should include a more diverse mix of lensed and unlensed
DSFGs.  On the other hand, this sample is selected from a survey with an area
that is 200 times larger than that of ALESS.  It is no surprise then, that the
median $S_{500}$ in our sample is $\sim3.5$ times brighter than the median
$S_{500}$ in ALESS.  Our ALMA sample opens a new window of discovery space on
the bright end of the DSFG luminosity function.

@@

\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the H-ATLAS
phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
(log of number of galaxies shown in grayscale).  The sample of HerMES sources
in this paper are shown with green squares (the ``ALMA sample'').  The very
bright {\it Herschel} DSFGs from \citet{Bussmann:2013lr} (the ``SMA sample'')
are shown by red circles, and the overall sample of candidate lensed {\it
Herschel} DSFGs are highlighted by yellow circles.  Lensed SMGs discovered by
the SPT that have published lens models are represented by cyan stars
\citep{Hezaveh:2013fk}.  A magenta diamond shows the location in this diagram
of the stacked signal from ALESS DSFGs.  Representative error bars are shown in
the lower left corner.  The ALMA sample fills the gap in 500$\,\mu$m flux
density space between SMA/SPT and ALESS samples.} \label{fig:sample}

@@

In detail, two of the sources in the ALMA sample (HXMM01 and HXMM02) overlap
with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr} as well as with
the SMA sample in \citet{Bussmann:2013lr}.  A further 8 appear in the
``Supplementary sample'' in \citet{Wardlow:2013lr}.  The remainder have
$S_{500} < 80\,$mJy and thus do not appear in \citet{Wardlow:2013lr}.

@@

Table~\ref{tab:position} provides reference data for the ALMA sample, including
centroid positions measured from the ALMA 870$\, \mu$m imaging (see
section~\ref{sec:almaobs}).

@@

ALMA data were obtained during Cycle~0 over the from 2012 June to 2012 December
(Program 2011.0.00539.S; PI: D. Riechers).  The observations were carried out
in good 870$\,\mu$m weather conditions which resulted in typical system
temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
10\,$deg.  Each target was observed until an rms noise level near the phase
center of $\sigma \approx 0.2\,$mJy was achieved.  This typically required 10
minutes of on-source integration time.  For the observations targeting the
CDFS, ELAISS, and COSMOS fields, the data reach $\sigma \approx 0.14\,$mJy.
The number of antennas used varied from 15 to 25.  The antennas were configured
with baseline lengths of 20$\,$m to 400$\,$m, providing a synthesized beamsize
of $\approx 0\farcs5 \times 0\farcs4$ FWHM while ensuring that no flux was
resolved out by the interferometer (since our targets all have size scales
smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple targets
in a single track was used to optimize the {\it uv} coverage.

The quasars J0403$-$360, J2258$-$279, B0851$+$202, and J2258$-$279 were used
for bandpass and pointing calibration.  The quasars J0403$-$360, J0106$-$405,
J0519$-$454, J1008$+$063, and J0217$+017$ were used for amplitude and phase
gain calibration.  The following solar system objects were used for absolute
flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
targets) and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
object was observed.  Instead, J2258$-$279 was used for absolute flux
calibration, with the flux fixed according to a measurement made two days prior
to the observations of HELAISS02.

@@

We used the Common Astronomy Software Applications (CASA, version 4.2.1)
package to investigate the quality of the reduced data provided by the North
American ALMA Science Center (NAASC).  Overall, the quality of the processed
data from the NAASC was very high.  We achieved a significant improvement in
the case of the ADFS and XMM targets by excluding datasets with moderate
$T_{\rm sys}$ and poor phase fluctuations.  For a handful of targets with peak
signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
improvement in S/N by using the CASA {\sc selfcal} task with the clean component
model as input to improve the phase gain corrections.  Finally, we updated the
absolute flux calibration to use the Butler-JPL-Horizons 2012 solar system
models.

For imaging, we used the CASA {\sc Clean} task with Briggs weighting and robust
= $+$0.5 to achieve an optimal balance between sensitivity and spatial
resolution.  We selected the multi-frequency synthesis option to optimize {\it
uv} coverage.  We designed custom masks for each target in CASA to ensure that
only regions with high S/N were considered during the cleaning process.

Figure~\ref{fig:imaging} presents our ALMA images (colorscale) in comparison to
the {\it Herschel} SPIRE images (black-white contours) originally used to
select the targets and noted in each panel as either 250$\,\mu$m, 350$\,\mu$m,
or 500$\,\mu$m.  Each panel is centered on the phase center of the ALMA
observations of that target and a white circle traces the FWHM of the primary
beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  All flux density measurements
given in this paper have been corrected for the primary beam by dividing the
total flux density by the primary beam correction factor at the center of the
source.  This is a valid approach because all sources have sizes $< 1\arcsec$,
such that the variation in the primary beam correction factor across the source
is insignificant.  A white dashed box represents the region of each image that
is shown in greater detail in Figure~\ref{fig:uvmodels}.

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of
the program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01,
HADFS11, HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each
of these targets were observed for a total of 9$\,$minutes of on-source
integration time in each of $u$, $g$, $r$, $i$, and $z$.  The observations were
obtained during dark time in with adequate seeing conditions (image quality in
the 85th percentile, corresponding to $\approx 1.1\arcsec$.

The data were reduced using the standard {\sc IRAF} Gemini GMOS reduction
routines, following the standard GMOS-S reduction steps in the example taken
from the Gemini observatory webpage
\footnote{http://www.gemini.edu/sciops/data-and-results/processing-software/getting-started\#gmos}.

We used the Sloan Digital Sky Survey (SDSS) or the 2 Micron All Sky Survey
(2MASS) to align the Gemini-S images to a common astrometric frame of
reference.  This imposes an rms uncertainty in the absolute astrometry of
$0\farcs2$ and $0\farcs4$ for SDSS and 2MASS, respectively.  The
astrometrically calibrated Gemini-S images served as the basis for aligning
higher resolution, smaller field-of-view imaging from {\it HST} or Keck (when
available) that were originally presented in \citet{Calanog:2014lr}.

@@

\caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
DSFGs (images have not been corrected for primary beam attenuation).  Contours
(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
size of the ALMA synthesized beam is shown in the lower left corner of each
panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
squares identify the regions of each image that are shown in greater detail in
Figure~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}

@@

An interferometer measures visibilities at discrete points in the {\it uv}
plane.  This is why pixel-to-pixel errors in the inverted and deconvolved
surface brightness map of an astronomical source are correlated.  The best way
to deal with this situation is to compare model and data visibilities rather
than surface brightness maps.  The methodology used in this paper is similar in
many aspects to that used in \citet{Bussmann:2012lr}, who presented the first
lens model derived from a visibility-plane analysis of interferometric imaging
of a strongly lensed DSFG discovered in wide-field submm surveys as well as
\citet{Bussmann:2013lr}, who extended this work to a statistically significant
sample of 30 objects.  It also bears some resemblence to the method used in
\citet{Hezaveh:2013fk}, who undertake lens modeling of interferometric data in
the visibility plane.  We summarize important information on the methodology
here, taking care to highlight where any differences occur between this work and
that of our previous efforts.

We created and made publicly available custom software, called {\sc uvmcmcfit},
that is capable of modeling all of the ALMA sources in this paper efficiently
and reliably.

Sources are assumed to be elliptical Gaussians that are parameterized by the
following six free parameters: the position of the source (relative to the
primary lens if a lens is present) ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S_{\rm in}$), the
effective radius intermediate axis length ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm
s}}$), the axial ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position
angle ($\phi_{\rm s}$, degrees east of north).  The use of an elliptical
Gaussian represents a simplification from the S\'ersic profile
\citep{1968adga.book.....S}  that is permitted based on the relatively weak
constraints on the S\'ersic index found in our previous work
\citep{Bussmann:2012lr, Bussmann:2013lr}.

>>>>

\title{HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty
Star-forming Galaxies}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  Combined with our previous work on brighter {\it
    Herschel} sources, the lens models presented here constrain the shape of
    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
    break down into multiple ALMA counterparts, consistent with previous
    research indicating that the multiplicity rate is high in bright sources
    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
    our {\it Herschel} targets are located much closer to each other than ALMA
    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
    Theoretical models underpredict the excess number of sources with small
    separations seen in our ALMA sample.  The high multiplicity rate and low
    projected separations between sources seen in our sample argue in favor of
    interactions and mergers plausibly driving both the prodigious emission
    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
    8\,$mJy.

@@

Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimeter
(sub-mm) wavelengths are generally known as dusty star-forming galaxies
\citep[DSFGs; for a recent review, see][]{Casey:2014lr}.  They cover a wide
range in redshift from $z \sim 0.5$ to $z > 6$ \citep{2005ApJ...622..772C,
Casey:2012qy, Messias:2014fk, Riechers:2013lr}, with a significant component at
$z \sim 2$ \citep{Casey:2012uq, Bothwell:2013lr}, when they represent the most
FIR-luminous objects in existence during this epoch.   They are usually
signposts of significant over-densities \citep{Daddi:2009qy, Capak:2011qy}
\citep[c.f.][]{Robson:2014xy} and likely represent the formative stages of the
most massive elliptical galaxies found in the local Universe
\citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute an
important component of the overall galaxy population at $z \sim 2$
\citep[e.g.,][]{Magnelli:2011ul}, when the star-formation rate density in the
Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.

@@

We here present Atacama Large Millimeter/submillimeter Array (ALMA) Cycle~0
imaging at 870$\,\mu$m of a sample of 29 HerMES DSFGs.
%Our targets were selected to be significantly fainter than those reported in
%\citet{Bussmann:2013lr}, so they include a larger number of unlensed or weakly
%lensed ($\mu_{870} < 2$) sources.  
Three aspects of our dataset make it uniquely suited to improving our
understanding of the bright end of the intrinsic DSFG luminosity function.
First, the sample occupies a distinct regime in flux density between the
brightest {\it Herschel} DSFGs (almost all of which are lensed) and much
fainter DSFGs found in ground-based surveys \citep[most of which are expected
to be unlensed; e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely
sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
\citep[which was not the case in previous similar studies with shallower imaging;
e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
angular resolutions are $0\farcs45$ and nearly all sources detected by ALMA are
spatially resolved.

We also obtained Gemini-South optical imaging to complement our existing set
of ancillary multi-wavelength imaging.  We use those data in this paper to
identify lensing galaxies, which are typically early-types with little on-going
star-formation and therefore exhibit very weak sub-mm emission.

In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
Gemini-South imaging.  Section~\ref{sec:modelfits} presents our model fitting
methodology and model fits for all ALMA sources (lensed and unlensed) using {\sc
uvmcmcfit}, a publicly available
\footnote{\url https://github.com/sbussmann/uvmcmcfit} modified version of the
visibility plane lens modeling software used in \citet{Bussmann:2012lr,
Bussmann:2013lr}.  Results on the effect of lensing for the observed properties
of the {\it Herschel} DSFGs in our sample, as well as the multiplicity rate and
typical angular separation between sources after delensing the ALMA sources,
appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
$\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
end of the DSFG luminosity function in Section~\ref{sec:discuss}.  Finally, we
present our conclusions in Section~\ref{sec:conclusions}.

@@

The starting point for the sample selection is source extraction and
photometry.  For the objects in this paper, individual catalogs were generated
for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.

The sample was selected to be a complete, flux-limited set of objects
satisfying $S_{500} > 95\,$mJy that are not known radio AGN, nearby late-type
galaxies, or Galactic emission. The selection was designed to assemble a large
sample of lensed galaxies in the ALMA-accesible HerMES fields, and was
constructed from the SUSSEXtractor catalogs, which were available prior to the
ALMA Cycle~0 deadline.  Subsequently, improved efforts to deblend SPIRE
photometry at 500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced
that formed the basis of the lens selection criteria used in
\citet{Wardlow:2013lr}.  As a result of the improved deblending algorithms in
the StarFinder catalogues and \citet{Wardlow:2013lr} a number of objects in our
sample have significantly lower $S_{500}$ values in the StarFinder catalog than
in the original SUSSEXtractor catalogs.  This and further investigation into
the StarFinder catalogs shows that their original flux was boosted by blending
with nearby sources rather than by gravitational lensing.  For this reason, the
objects in this sample comprise a combination of lenses and blends of multiple
sources.

@@

Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
clearly apart from the very bright {\it Herschel} DSFGs that are selected to
have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
the sample in this paper should include a more diverse mix of lensed and
unlensed DSFGs.  On the other hand, this sample is selected from a survey with
an area that is 200 times larger than that of the Large Apex Bolometer Camera
Extended Chandra Deep Field Survey \citep[LESS][]{Weis:2009ly}.  It is no
surprise then, that the median $S_{500}$ in our sample is $\sim3.5$ times
brighter than the median $S_{500}$ in the sample of ALMA-detected sources in
LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it Herschel}-ALMA sample
opens a new window of discovery space on the bright end of the DSFG luminosity
function.

@@

\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the HerMES phase~I
catalog with declination $< +2\,^\circ$ and signal to noise ratio greater than
1 at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m (log of number of galaxies shown
in grayscale).  The sample of HerMES sources in this paper are shown with green
squares (``{\it Herschel}-ALMA'').  The very bright {\it Herschel} DSFGs from
\citet{Bussmann:2013lr} (``{\it Herschel}-SMA'') are shown by red circles, and
lensed SMGs discovered by the SPT that have published lens models
(``SPT-ALMA'') are represented by cyan stars \citep{Hezaveh:2013fk}.  A magenta
diamond shows the location in this diagram of the stacked signal from ALESS
DSFGs.  Representative error bars are shown in the lower left corner.  The {\it
Herschel}-ALMA sample fills the gap in 500$\,\mu$m flux density space between
50-100$\,$mJy.} \label{fig:sample}

@@

In detail, two of the sources in the {\it Herschel}-ALMA sample (HXMM01 and
HXMM02) overlap with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr}
as well as with the {\it Herschel}-SMA sample in \citet{Bussmann:2013lr}.  A
further eght appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
The remainder have $S_{500} < 80\,$mJy and thus do not appear in
\citet{Wardlow:2013lr}.

@@

Table~\ref{tab:position} provides reference data for the {\it Herschel}-ALMA sample, including
centroid positions measured from the ALMA 870$\, \mu$m imaging (see
Section~\ref{sec:almaobs}).

@@

ALMA data were obtained during Cycle~0 over the from 2012 June to 2012 December
(Program 2011.0.00539.S; PI: D. Riechers).  The observations were carried out
in good 870$\,\mu$m weather conditions, which resulted in typical system
temperatures of $T_{\rm sys} \approx 130\,$K and phase fluctuations of $\sim
10\,^\circ$.  Each target was observed until an rms noise level near the phase
center of $\sigma \approx 0.2\,$mJy was achieved.  This typically required 10
minutes of on-source integration time.  For the observations targeting the
CDFS, ELAISS, and COSMOS fields, the data reach $\sigma \approx 0.14\,$mJy.
The number of antennas used varied from 15 to 25.  The antennas were configured
with baseline lengths of 20$\,$m to 400$\,$m, providing a synthesized beamsize
of $\approx 0\farcs5 \times 0\farcs4$ FWHM while ensuring that no flux was
resolved out by the interferometer (since our targets all have size scales
smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple targets
in a single track was used to optimize the {\it uv} coverage.

The quasars J0403$-$360, J2258$-$279, B0851$+$202, and J2258$-$279 were used
for bandpass and pointing calibration.  The quasars J0403$-$360, J0106$-$405,
J0519$-$454, J1008$+$063, and J0217$+017$ were used for amplitude and phase
gain calibration.  The following solar system objects were used for absolute
flux calibration: Callisto (CDFS targets); Neptune (XMM targets); Titan (COSMOS
targets); and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
object was observed.  Instead, J2258$-$279 was used for absolute flux
calibration, with the flux fixed according to a measurement made two days prior
to the observations of HELAISS02.

@@

We used the Common Astronomy Software Applications (CASA, version 4.2.1)
package to re-reduce the data provided by the North American ALMA Science
Center (NAASC).  We found that the quality of the processed data from the NAASC
was very high.  However, we achieved a significant improvement in the case of
the ADFS and XMM targets by excluding data sets with moderate $T_{\rm sys}$ and
poor phase fluctuations.  For a handful of targets with peak signal-to-noise
ratio (S/N) greater than 20, we obtained a $\approx 10\%$ improvement in S/N by
using the CASA {\sc selfcal} task with the clean component model as input to
improve the phase gain corrections.  Finally, we updated the absolute flux
calibration to use the Butler-JPL-Horizons 2012 solar system models
\footnote{\url
https://science.nrao.edu/facilities/alma/aboutALMA/Technology/ALMA\_Memo\_Series/alma594/abs594}.

For imaging, we used the CASA {\sc Clean} task with Briggs weighting and ``robust
= $+$0.5'' to achieve an optimal balance between sensitivity and spatial
resolution.  We selected the multi-frequency synthesis option to optimize {\it
uv} coverage.  We designed custom masks for each target in CASA to ensure that
only regions with high S/N were considered during the cleaning process.

Figure~\ref{fig:imaging} presents our ALMA images (color scale) in comparison to
the {\it Herschel} SPIRE images (black-white contours) originally used to
select the targets and noted in each panel as either 250$\,\mu$m, 350$\,\mu$m,
or 500$\,\mu$m.  Each panel is centered on the phase center of the ALMA
observations of that target and a white circle traces the FWHM of the primary
beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  All flux density measurements
given in this paper have been corrected for the primary beam by dividing the
total flux density by the primary beam correction factor at the center of the
source.  This is a valid approach because all sources have sizes $< 1\arcsec$,
such that the variation in the primary beam correction factor across the source
is insignificant.  A white dashed box represents the region of each image that
is shown in greater detail in Figure~\ref{fig:uvmodels}.

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of
the program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at redshifts below unity and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging, thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01,
HADFS11, HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each
of these targets were observed for a total of 9$\,$minutes of on-source
integration time in each of $u$, $g$, $r$, $i$, and $z$.  The observations were
obtained during dark time in adequate seeing conditions (image quality in
the 85th percentile, corresponding to $\approx 1.1\arcsec$).

The data were reduced using the standard {\sc IRAF} Gemini GMOS reduction
routines, following the standard GMOS-S reduction steps in the example taken
from the Gemini observatory webpage
\footnote{\url http://www.gemini.edu/sciops/data-and-results/processing-software/getting-started\#gmos}.

We used the Sloan Digital Sky Survey (SDSS) or the 2 Micron All Sky Survey
(2MASS) to align the Gemini-S images to a common astrometric frame of
reference.  This imposes an rms uncertainty in the absolute astrometry of
$0\farcs2$ and $0\farcs4$ for SDSS and 2MASS, respectively.  The
astrometrically calibrated Gemini-S images served as the basis for aligning
higher resolution, smaller field-of-view imaging from {\it HST} or Keck (when
available), which were originally presented in \citet{Calanog:2014lr}.

@@

\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of HerMES
DSFGs (images have not been corrected for primary beam attenuation).  Contours
(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
size of the ALMA synthesized beam is shown in the lower left corner of each
panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
squares identify the regions of each image that are shown in greater detail in
Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}

@@

An interferometer measures visibilities at discrete points in the {\it uv}
plane.  This is why pixel-to-pixel errors in the inverted and deconvolved
surface brightness map of an astronomical source are correlated.  The best way
to deal with this situation is to compare model and data visibilities rather
than surface brightness maps.  The methodology used in this paper is similar in
many aspects to that used in \citet{Bussmann:2012lr}, who presented the first
lens model derived from a visibility-plane analysis of interferometric imaging
of a strongly lensed DSFG discovered in wide-field submm surveys as well as in
\citet{Bussmann:2013lr}, where this work was extended to a
statistically significant sample of 30 objects.  It also bears some resemblence
to the method used in \citet{Hezaveh:2013fk}, who undertake lens modeling of
interferometric data in the visibility plane.  We summarize important
information on the methodology here, taking care to highlight where any
differences occur between this work and that of our previous efforts.

We created and made publicly available custom software, called {\sc uvmcmcfit},
which is capable of modeling all of the ALMA sources in this paper efficiently
and reliably.

Sources are assumed to be elliptical Gaussians that are parameterized by the
following six free parameters: the position of the source (relative to the
primary lens if a lens is present, $\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S_{\rm in}$), the
effective radius length ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$, degrees east of north).  The use of an elliptical Gaussian
represents a simplification from the S\'ersic profile
\citep{1968adga.book.....S}  that is permitted based on the relatively weak
constraints on the S\'ersic index found in our previous work
\citep{Bussmann:2012lr, Bussmann:2013lr}.

When an intervening galaxy (or group of galaxies) is present along the line of
sight, {\sc uvmcmcfit} accounts for the deflection of light caused by this
structure using a simple ray-tracing routine that is adopted from a Python
routine written by A.~Bolton
\footnote{http://www.physics.utah.edu/$\sim$bolton/python\_lens\_demo/}.  This
represents a significant difference from \citet{Bussmann:2012lr} and
\citet{Bussmann:2013lr}, where we used the publicly available {\sc Gravlens}
software \citep{Keeton:2001lr} to map emission from the source plane to the
image plane for a given lensing mass distribution.  {\sc Gravlens} has a wide
range of lens mass profiles as well as a sophisticated algorithm for mapping
source plane emission to the image plane, but it also comes with a significant
input/output penalty that makes parallel computing prohibitively expensive.
For example, modeling a simple system comprising one lens and one source
typically required 24-48$\,$hours using the old software, whereas the same
system can be modeled in less than one hour with the pure-Python code (tests of
the Bolton ray-tracing routine indicate it produces results consistent with
{\sc Gravlens}).  The use of pure-Python code for tracing the deflection of
light rays is a critical component of making {\sc uvmcmcfit} computationally
feasible.
